### 2023-04-11 article.tex
Add author biography

>>>>

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Author biography}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

Dr. Bilderbeek has worked in computational biology for more than a decade.
Currently, he works for the National Bioinformatics Infrastructure Sweden (NBIS)
in Uppsala, Sweden, 
as an application expert and trainer, with a focus on reproducible research.
All his work can be found on GitHub at \url{https://github.com/richelbilderbeek}
and his YouTube channel.
